No-click browsing of large hierarchical data

### 2020-03-07 paper/HCC2020/paper.tex
...

%
% HCC用にIEEEフォーマットにしたもの
%
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

@@

@@

The simplest input device for Gear may be keyboards and push buttons.
We tried using arrow keys on a PC, and it works fine.
Various HID devices\footnote{
  https://en.wikipedia.org/wiki/Human\_interface\_device
} are available on the market, and
all such devices can be used as an input device for Gear.
For example, a foot switch for turning music score pages\footnote{
  airturn pedpro
} can be used as the input device for Gear.
Even a special foot pedal can be used for Gear (Figure \ref{footswitch}).

@@

@@

Since the idea of Gear interface is so simple,
we have been wondering if the same idea existed in the past.
We are almost sure that The Gear interface had never been popular before,
and we could not find a similar method in the patent database.

>>>>

%
% HCC用にIEEEフォーマットにしたもの
%
% 参考文献に適当なものを入れたい
%  Dynamic Queryとか no-click browsingが気持ちよい理由
%
%  https://dl.acm.org/doi/abs/10.1145/964696.964706 五十嵐氏の カスケーディングメニューのトラバース
%
% tree traverseという言葉を使いたい
%
% Dasher, LensBar
%
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

@@

% Input device, Information navigation, No-click browsing, Hierarchical data, Gear, Serencast

@@

The simplest input device for Gear may be keyboards and push buttons.
Gear works pretty comfortably with arrow keys on a PC.
Various HID devices\footnote{
  https://en.wikipedia.org/wiki/Human\_interface\_device
} are available on the market, and
all such devices can be used as an input device for Gear.
For example, a foot switch for turning music score pages\footnote{
  airturn pedpro
} can be used as the input device for Gear.
Even a special foot pedal can be used for Gear (Figure \ref{footswitch}).

@@

\begin{figure}[H]
\centerline{
  \includegraphics[width=38mm,bb=0 0 188 188]{figures/treeview.png}
}
\caption{A TreeView example.}
\label{treeview}
\end{figure}

@@

Since the idea of Gear interface is so simple,
we have been wondering if the same idea existed in the past.
%
We could not find a research paper on 
navigation techniques based on two keys.
Many key-based navigation techniques are found on patent database,
but we could not find a navigation method based on two keys.
We are almost sure that The Gear interface had never been popular before,
